Creating Haul-out Timeline Input Data

### 2021-06-30 analysis/scripts/get_data/creating_input_data.Rmd

```{r}
if (params$make_data) {
source(here::here('analysis/scripts/get_data/make_data.R'))
} else {
  load(here::here('data/locs_sf.Rdata'))
  load(here::here('data/timeline_data.Rdata'))
  load(here::here('data/tbl_percent_locs.Rdata'))
}
```

>>>>

```{r}
if (params$make_data) {
  source(here::here('analysis/scripts/get_data/make_data.R'))
  save(locs_sf, file = here::here('data/locs_sf.Rdata'))
  save(timeline_data, file = here::here('timeline_data.Rdata'))
} else {
  load(here::here('data/locs_sf.Rdata'))
  load(here::here('data/timeline_data.Rdata'))
  load(here::here('data/tbl_percent_locs.Rdata'))
}
```
